Fluent statistical computing interfaces for biological data analysis

### 2020-08-04 Rmd/00-e-preface.Rmd
update text
don't number preface
addresses comments and closes #10
update preface and rebuild

Chapter \@ref(ch:plyranges) has been published in _Genome Biology_. It
won the ACEMS Business Analytics Prize for Best Paper in 2019. Chapter \@ref(ch:fluentGenomics) has been published in _F1000 Research_.  Chapter
\@ref(ch:intron) is based on my software contributions to the submitted
article @Lee2019-mf. Chapter \@ref(ch:embedding) has not been submitted yet.

## Open Research

This thesis has been written using R Markdown with the **bookdown**
package [@Xie2016-oa; @Xie2017-ke]. All materials required to build the
thesis from source can be obtained from https://github.com/sa-lee/thesis. An
online version of the thesis is available at https://sa-lee.github.io/thesis.

>>>>

This thesis has been written using R Markdown with the **bookdown**
package [@Xie2016-oa; @Xie2017-ke]. The **renv** package
has been used to create a reproducible environment to build the thesis from source (available at https://github.com/sa-lee/thesis ) [@renv]. An online version of the thesis is available to read at https://sa-lee.github.io/thesis.

Chapter \@ref(ch:plyranges) has been published in _Genome Biology_. It
won the ACEMS Business Analytics Prize for Best Paper in 2019. Chapter \@ref(ch:fluentGenomics) has been published in _F1000 Research_.  Chapter
\@ref(ch:intron) is based on my software contributions to the submitted
article @Lee2019-mf. Chapter \@ref(ch:tsne) has not been submitted.
